Against Spurious Understanding: Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}

### 2024-01-31 main.tex
Updates from Overleaf

\begin{abstract}
Humans have a tendency to place a `human' like quality in the objects around them. Giving your car a name or talking to your pet, such that you believe they understand you in a human way. This behavior is also seeing traction in Machine Learning (ML), where the idea of sentience is being placed upon Large Language Models (LLMs). In this position paper, we discuss why humans invariably anthropomorphize onto various objects and how the search for Artificial General Intelligence (AGI) is pushing recent literature to over emphasis sentience. To combat this, we provide a short study that investigates the latent space of models, demonstrating that the discovery of patterns in latent spaces should not be a surprising outcome. Finally, we discuss how the popularity in media and the race for AGI enforces over-interpretation of consciousness in the models we use.

>>>>

\begin{abstract}
Humans have a tendency to place a `human' like quality in the objects around them. Giving your car a name or talking to your pet, such that you believe they understand you in a human way. This behavior is also seeing traction in Machine Learning (ML), where the idea of sentience is being placed upon Large Language Models (LLMs). In this position paper, we discuss why humans invariably anthropomorphize onto various objects and how the search for Artificial General Intelligence (AGI) is pushing recent literature to overemphasize sentience. To combat this, we provide a short study that investigates the latent space of models, demonstrating that the discovery of patterns in latent spaces should not be a surprising outcome. Finally, we discuss how the popularity in media and the race for AGI enforces over-interpretation of consciousness in the models we use.
